---
title: "Error Checks per Individual Participant"
author: "Raphael Q. Gastrock"
date: "2024-02-05"
output:
  pdf_document:
    toc: true
    toc_depth: '1'
  # html_document:
  #   toc: true
  #   toc_depth: 1
  #   toc_float: true
---

```{r, warning=FALSE, message=FALSE}
source('ana/shared.R')
source('ana/learningRates.R')
source('ana/errorChecks.R')
```

# Trial indices for small and large errors: Fixed Rotation

```{r}
getROTErrorIndices()
```

# Trial indices for small and large errors: Mirror

```{r}
plotMIRErrorIndices()
```

# Aligned and Small Errors: Fixed Rotation

Every point is a participant (N=32), which contains the median aligned angular error and median small magnitude angular error. Small errors are just the lower 1/3 of all perturbation trials.

```{r}
getGroupALROTAngularErrors()
```

# Aligned and Small Errors: Mirror

Plots are split according to different target locations (perfect compensation at 15, 30, and 45 degrees).

```{r, fig.width=20, fig.height=6}
getGroupALMIRAngularErrors()
```

# Aligned and Small Errors: Random (Before rotation)

Plots are split according to different target locations (perfect compensation at 15, 25, and 35 degrees).

```{r, fig.width=20, fig.height=6}
getGroupALRDMROTAngularErrors()
```

# Aligned and Small Errors: Random (Before mirror)

Plots are split according to different target locations (perfect compensation at 15, 25, and 35 degrees).

```{r, fig.width=20, fig.height=6}
getGroupALRDMMIRAngularErrors()
```




<!-- # Aligned and different Fixed Rotation error magnitudes -->

<!-- ```{r, fig.width=20, fig.height=6} -->
<!-- getALROTAngularErrors() -->
<!-- ``` -->

<!-- # Fixed Rotation error magnitudes across trials -->

<!-- ```{r} -->
<!-- getROTAngularErrorMagnitudeAcrossTrials() -->
<!-- ``` -->

<!-- # Aligned and different Mirror error magnitudes: 15 degrees compensation -->

<!-- ```{r, fig.width=20, fig.height=6} -->
<!-- getALMIRAngularErrors(angles=c(15)) -->
<!-- ``` -->

<!-- # Mirror error magnitudes across trials: 15 degrees compensation -->

<!-- ```{r} -->
<!-- getMIRAngularErrorMagnitudeAcrossTrials(angles=c(15)) -->
<!-- ``` -->

<!-- # Aligned and different Mirror error magnitudes: 30 degrees compensation -->

<!-- ```{r, fig.width=20, fig.height=6} -->
<!-- getALMIRAngularErrors(angles=c(30)) -->
<!-- ``` -->

<!-- # Mirror error magnitudes across trials: 30 degrees compensation -->

<!-- ```{r} -->
<!-- getMIRAngularErrorMagnitudeAcrossTrials(angles=c(30)) -->
<!-- ``` -->

<!-- # Aligned and different Mirror error magnitudes: 45 degrees compensation -->

<!-- ```{r, fig.width=20, fig.height=6} -->
<!-- getALMIRAngularErrors(angles=c(45)) -->
<!-- ``` -->

<!-- # Mirror error magnitudes across trials: 45 degrees compensation -->

<!-- ```{r} -->
<!-- getMIRAngularErrorMagnitudeAcrossTrials(angles=c(45)) -->
<!-- ``` -->

<!-- # Aligned and different Random (before rotation) error magnitudes: 15 degrees compensation -->

<!-- ```{r, fig.width=20, fig.height=6} -->
<!-- getALRDMROTAngularErrors(angles=c(15)) -->
<!-- ``` -->

<!-- # Random (before rotation) error magnitudes across trials: 15 degrees compensation -->

<!-- ```{r} -->
<!-- getRDMROTAngularErrorMagnitudeAcrossTrials(angles=c(15)) -->
<!-- ``` -->

<!-- # Aligned and different Random (before rotation) error magnitudes: 25 degrees compensation -->

<!-- ```{r, fig.width=20, fig.height=6} -->
<!-- getALRDMROTAngularErrors(angles=c(25)) -->
<!-- ``` -->

<!-- # Random (before rotation) error magnitudes across trials: 25 degrees compensation -->

<!-- ```{r} -->
<!-- getRDMROTAngularErrorMagnitudeAcrossTrials(angles=c(25)) -->
<!-- ``` -->

<!-- # Aligned and different Random (before rotation) error magnitudes: 35 degrees compensation -->

<!-- ```{r, fig.width=20, fig.height=6} -->
<!-- getALRDMROTAngularErrors(angles=c(35)) -->
<!-- ``` -->

<!-- # Random (before rotation) error magnitudes across trials: 35 degrees compensation -->

<!-- ```{r} -->
<!-- getRDMROTAngularErrorMagnitudeAcrossTrials(angles=c(35)) -->
<!-- ``` -->

<!-- # Aligned and different Random (before mirror) error magnitudes: 15 degrees compensation -->

<!-- ```{r, fig.width=20, fig.height=6} -->
<!-- getALRDMMIRAngularErrors(angles=c(15)) -->
<!-- ``` -->

<!-- # Random (before mirror) error magnitudes across trials: 15 degrees compensation -->

<!-- ```{r} -->
<!-- getRDMMIRAngularErrorMagnitudeAcrossTrials(angles=c(15)) -->
<!-- ``` -->

<!-- # Aligned and different Random (before mirror) error magnitudes: 25 degrees compensation -->

<!-- ```{r, fig.width=20, fig.height=6} -->
<!-- getALRDMMIRAngularErrors(angles=c(25)) -->
<!-- ``` -->

<!-- # Random (before mirror) error magnitudes across trials: 25 degrees compensation -->

<!-- ```{r} -->
<!-- getRDMMIRAngularErrorMagnitudeAcrossTrials(angles=c(25)) -->
<!-- ``` -->

<!-- # Aligned and different Random (before rotation) error magnitudes: 35 degrees compensation -->

<!-- ```{r, fig.width=20, fig.height=6} -->
<!-- getALRDMMIRAngularErrors(angles=c(35)) -->
<!-- ``` -->

<!-- # Random (before rotatiion) error magnitudes across trials: 35 degrees compensation -->

<!-- ```{r} -->
<!-- getRDMMIRAngularErrorMagnitudeAcrossTrials(angles=c(35)) -->
<!-- ``` -->