---
title: "Error Checks per Individual Participant"
author: "Raphael Q. Gastrock"
date: "2024-02-05"
output:
  pdf_document:
    toc: true
    toc_depth: '1'
  # html_document:
  #   toc: true
  #   toc_depth: 1
  #   toc_float: true
---

This document contains plots and some correlations regarding error sizes in the different trial types. Individual data show high variability of small and large errors within and across participants. That is, not every individual shows larger errors early in training and smaller error at the end of training. As such, we have decided to analyze early vs. late training and small vs. large errors separately (see MNE-PythonProcessingScripts R ntbk).

```{r, warning=FALSE, message=FALSE}
source('ana/shared.R')
source('ana/learningRates.R')
source('ana/errorChecks.R')
```

# Trial indices for small and large errors: Fixed Rotation

```{r}
getROTErrorIndices()
```

# Trial indices for small and large errors: Mirror

```{r}
plotMIRErrorIndices()
```

# Aligned and Small Errors: Fixed Rotation

Every point is a participant (N=32), which contains the median aligned angular error and median small magnitude angular error. Small errors are just the lower 1/3 of all perturbation trials.

```{r}
getGroupALROTAngularErrors()
```

# Aligned and Small Errors: Mirror

Plots are split according to different target locations (perfect compensation at 15, 30, and 45 degrees).

```{r, fig.width=20, fig.height=6}
getGroupALMIRAngularErrors()
```

# Aligned and Small Errors: Random (Before rotation)

Plots are split according to different target locations (perfect compensation at 15, 25, and 35 degrees).

```{r, fig.width=20, fig.height=6}
getGroupALRDMROTAngularErrors()
```

# Aligned and Small Errors: Random (Before mirror)

Plots are split according to different target locations (perfect compensation at 15, 25, and 35 degrees).

```{r, fig.width=20, fig.height=6}
getGroupALRDMMIRAngularErrors()
```




<!-- # Aligned and different Fixed Rotation error magnitudes -->

<!-- ```{r, fig.width=20, fig.height=6} -->
<!-- getALROTAngularErrors() -->
<!-- ``` -->

<!-- # Fixed Rotation error magnitudes across trials -->

<!-- ```{r} -->
<!-- getROTAngularErrorMagnitudeAcrossTrials() -->
<!-- ``` -->

<!-- # Aligned and different Mirror error magnitudes: 15 degrees compensation -->

<!-- ```{r, fig.width=20, fig.height=6} -->
<!-- getALMIRAngularErrors(angles=c(15)) -->
<!-- ``` -->

<!-- # Mirror error magnitudes across trials: 15 degrees compensation -->

<!-- ```{r} -->
<!-- getMIRAngularErrorMagnitudeAcrossTrials(angles=c(15)) -->
<!-- ``` -->

<!-- # Aligned and different Mirror error magnitudes: 30 degrees compensation -->

<!-- ```{r, fig.width=20, fig.height=6} -->
<!-- getALMIRAngularErrors(angles=c(30)) -->
<!-- ``` -->

<!-- # Mirror error magnitudes across trials: 30 degrees compensation -->

<!-- ```{r} -->
<!-- getMIRAngularErrorMagnitudeAcrossTrials(angles=c(30)) -->
<!-- ``` -->

<!-- # Aligned and different Mirror error magnitudes: 45 degrees compensation -->

<!-- ```{r, fig.width=20, fig.height=6} -->
<!-- getALMIRAngularErrors(angles=c(45)) -->
<!-- ``` -->

<!-- # Mirror error magnitudes across trials: 45 degrees compensation -->

<!-- ```{r} -->
<!-- getMIRAngularErrorMagnitudeAcrossTrials(angles=c(45)) -->
<!-- ``` -->

<!-- # Aligned and different Random (before rotation) error magnitudes: 15 degrees compensation -->

<!-- ```{r, fig.width=20, fig.height=6} -->
<!-- getALRDMROTAngularErrors(angles=c(15)) -->
<!-- ``` -->

<!-- # Random (before rotation) error magnitudes across trials: 15 degrees compensation -->

<!-- ```{r} -->
<!-- getRDMROTAngularErrorMagnitudeAcrossTrials(angles=c(15)) -->
<!-- ``` -->

<!-- # Aligned and different Random (before rotation) error magnitudes: 25 degrees compensation -->

<!-- ```{r, fig.width=20, fig.height=6} -->
<!-- getALRDMROTAngularErrors(angles=c(25)) -->
<!-- ``` -->

<!-- # Random (before rotation) error magnitudes across trials: 25 degrees compensation -->

<!-- ```{r} -->
<!-- getRDMROTAngularErrorMagnitudeAcrossTrials(angles=c(25)) -->
<!-- ``` -->

<!-- # Aligned and different Random (before rotation) error magnitudes: 35 degrees compensation -->

<!-- ```{r, fig.width=20, fig.height=6} -->
<!-- getALRDMROTAngularErrors(angles=c(35)) -->
<!-- ``` -->

<!-- # Random (before rotation) error magnitudes across trials: 35 degrees compensation -->

<!-- ```{r} -->
<!-- getRDMROTAngularErrorMagnitudeAcrossTrials(angles=c(35)) -->
<!-- ``` -->

<!-- # Aligned and different Random (before mirror) error magnitudes: 15 degrees compensation -->

<!-- ```{r, fig.width=20, fig.height=6} -->
<!-- getALRDMMIRAngularErrors(angles=c(15)) -->
<!-- ``` -->

<!-- # Random (before mirror) error magnitudes across trials: 15 degrees compensation -->

<!-- ```{r} -->
<!-- getRDMMIRAngularErrorMagnitudeAcrossTrials(angles=c(15)) -->
<!-- ``` -->

<!-- # Aligned and different Random (before mirror) error magnitudes: 25 degrees compensation -->

<!-- ```{r, fig.width=20, fig.height=6} -->
<!-- getALRDMMIRAngularErrors(angles=c(25)) -->
<!-- ``` -->

<!-- # Random (before mirror) error magnitudes across trials: 25 degrees compensation -->

<!-- ```{r} -->
<!-- getRDMMIRAngularErrorMagnitudeAcrossTrials(angles=c(25)) -->
<!-- ``` -->

<!-- # Aligned and different Random (before rotation) error magnitudes: 35 degrees compensation -->

<!-- ```{r, fig.width=20, fig.height=6} -->
<!-- getALRDMMIRAngularErrors(angles=c(35)) -->
<!-- ``` -->

<!-- # Random (before rotatiion) error magnitudes across trials: 35 degrees compensation -->

<!-- ```{r} -->
<!-- getRDMMIRAngularErrorMagnitudeAcrossTrials(angles=c(35)) -->
<!-- ``` -->