---
title: "Error distributions"
author: "Raphael Q. Gastrock"
date: "2024-12-05"
output: 
  pdf_document:
    toc: true
    toc_depth: '4'
    #toc_float: true
---

This document contains plots for error distributions across perturbation types. We show plots for each individual participant.

```{r, warning=FALSE, message=FALSE}
source('ana/shared.R')
source('ana/learningRates.R')
source('ana/errorSizesERP.R')
source('ana/permutationTtest.R')
```

# Fixed rotation

To calculate angular error, we subtract angular hand deviation from the perturbation size (30-degrees for fixed rotation). For each participant, we sort the error magnitudes, then take the lower 40% (36 trials out of 90) of errors as small errors. Large errors are the upper 40% of error magnitudes.

```{r}
plotROTParticipantErrorDistributions()
```

# Mirror reversal

To calculate angular error, we subtract angular hand deviation from the perturbation size (either 15, 30, or 45 degrees for the mirror reversal). For each participant and perturbation size, we sort the error magnitudes, then take the lower 40% (12 trials out of 30) of errors as small errors. Large errors are the upper 40% of error magnitudes. Although we do this for each perturbation size, all "small" and all "large" trials are combined into one condition each, in analyzing the EEG data.

## Mirror reversal, 15-degree target
```{r}
plotMIRParticipantErrorDistributions(angles=15)
```

## Mirror reversal, 30-degree target
```{r}
plotMIRParticipantErrorDistributions(angles=30)
```

## Mirror reversal, 45-degree target
```{r}
plotMIRParticipantErrorDistributions(angles=45)
```

# Random rotation

To calculate angular error, we subtract angular hand deviation from the perturbation size (either 15, 25, or 35 degrees for the random rotation). For each participant and perturbation size, we sort the error magnitudes, then take the lower ~40% (7 trials out of 16) of errors as small errors. Large errors are the upper 40% of error magnitudes. Although we do this for each perturbation size, all "small" and all "large" trials are combined into one condition each, in analyzing the EEG data. Also, random rotation trials prior to either the rotation and mirror blocks are combined for EEG analyses, as these do not show differences behaviorally.

## Random before every rotation block, 15-degree target
```{r}
plotRDMROTParticipantErrorDistributions(angles=15)
```

## Random before every rotation block, 25-degree target
```{r}
plotRDMROTParticipantErrorDistributions(angles=25)
```

## Random before every rotation block, 35-degree target
```{r}
plotRDMROTParticipantErrorDistributions(angles=35)
```

## Random before every mirror block, 15-degree target
```{r}
plotRDMMIRParticipantErrorDistributions(angles=15)
```

## Random before every mirror block, 25-degree target
```{r}
plotRDMMIRParticipantErrorDistributions(angles=25)
```

## Random before every mirror block, 35-degree target
```{r}
plotRDMMIRParticipantErrorDistributions(angles=35)
```




