---
title: "Permutation Statistics Analyses"
author: "Raphael Q. Gastrock"
date: "2024-07-26"
output: 
  html_document:
    toc: true
    toc_depth: '4'
    toc_float: true
---

This document contains permutation tests conducted for both ERP and TFR analyses

```{r, warning=FALSE, message=FALSE}
source('ana/shared.R')
source('ana/learningRates.R')
source('ana/errorSizesERP.R')
source('ana/directionMoves.R')
source('ana/p3analysis.R')
source('ana/permutationTtest.R')
```


# ERP Analyses

## Early vs Late conditions

### Feedback-related Negativity (FRN)

This is time-locked to feedback onset. Analyses includes 10 fronto-central-parietal electrodes:

FCz, F3, Fz, F4, C3, Cz, C4, P3, Pz, P4

#### Comparison to aligned reaches (baseline)

```{r}
plotPermTestEarlyLateERPs()
```

#### Comparison between early and late training

```{r}
plotPermTestEarlyLateDiffWaves()
```

#### Comparison across perturbation types

```{r}
plotPermTestPTypeEarlyLateDiffWaves()
```

### P3 component

This is also time-locked to feedback onset, but only considers electrodes along the midline:

FCz, Fz, Cz, Pz

#### Comparison to aligned reaches (baseline)

```{r}
plotPermTestEarlyLateP3()
```

#### Comparison between early and late training

```{r}
plotPermTestEarlyLateDiffWavesP3()
```

#### Comparison across perturbation types

```{r}
plotPermTestPTypeEarlyLateDiffWavesP3()
```

### Lateralized Readiness Potential (LRP)

This is time-locked to the go signal onset, which is 1 second after target onset. Analyses includes C3 and C4 electrodes, and considers only reaches to the left or right side of the workspace.

#### Comparison to aligned reaches (baseline)

```{r}
plotPermTestEarlyLateLRPs()
```

#### Comparison between early and late training

```{r}
plotPermTestEarlyLateLRPDiffWaves()
```

#### Comparison across perturbation types

```{r}
plotPermTestPTypeEarlyLateLRPDiffWaves()
```

## Small vs Large conditions

### Feedback-related Negativity (FRN)

This is time-locked to feedback onset. Analyses includes 10 fronto-central-parietal electrodes:

FCz, F3, Fz, F4, C3, Cz, C4, P3, Pz, P4

#### Comparison to aligned reaches (baseline)

```{r}
plotPermTestSmallLargeERPs()
```

#### Comparison between early and late training

```{r}
plotPermTestSmallLargeDiffWaves()
```

#### Comparison across perturbation types

```{r}
plotPermTestPTypeSmallLargeDiffWaves()
```

### P3 component

This is also time-locked to feedback onset, but only considers electrodes along the midline:

FCz, Fz, Cz, Pz

#### Comparison to aligned reaches (baseline)

```{r}
plotPermTestSmallLargeP3()
```

#### Comparison between early and late training

```{r}
plotPermTestSmallLargeDiffWavesP3()
```

#### Comparison across perturbation types

```{r}
plotPermTestPTypeSmallLargeDiffWavesP3()
```

### Lateralized Readiness Potential (LRP)

This is time-locked to the go signal onset, which is 1 second after target onset. Analyses includes C3 and C4 electrodes, and considers only reaches to the left or right side of the workspace.

#### Comparison to aligned reaches (baseline)

```{r}
plotPermTestSmallLargeLRPs()
```

#### Comparison between early and late training

```{r}
plotPermTestSmallLargeLRPDiffWaves()
```

#### Comparison across perturbation types

```{r}
plotPermTestPTypeSmallLargeLRPDiffWaves()
```